### 2021-06-03 JSS/using_drtmle_jss.Rmd
porting over minor JSS changes from fork

---
documentclass: jss
author:
  - name: David Benkeser
    affiliation: Emory University
    address: |
      | 1518 Clifton Road, NE
      | Mailstop: 002-3AA
      | Atlanta, Georgia, 30322, U.S.A.
    email: \email{benkeser@emory.edu}
  - name: Nima Hejazi
    affiliation: University of California, Berkeley
    email: \email{nhejazi@berkeley.edu}
title:
  formatted: "Doubly-Robust Inference in R using \\pkg{drtmle}"
  plain: "Doubly-Robust Inference in R using drtmle"
  short: "\\pkg{drtmle}: Doubly-robust Inference"
keywords:
  formatted: [causal inference, machine learning, treatment effects, targeted minimum loss estimation]
  plain: [causal inference, machine learning, treatment effects, targeted minimum loss estimation]
preamble: >
  \usepackage{amsmath}
abstract: >
  Inverse probability of treatment weighted estimators and doubly-robust
  estimators (including augmented inverse probability of treatment weight and
  targeted minimum loss-based estimators) are widely used in causal inference to
  estimate and draw inference about the average effect of a treatment. As an
  intermediate step, these estimators require estimation of key nuisance
  parameters, which are often regression functions. Typically, regressions are
  estimated using maximum likelihood and parametric models. Confidence intervals
  and p-values may be computed based on standard asymptotic results, such as the
  central limit theorem, the delta method, and the nonparametric bootstrap. 
  However, in high-dimensional settings maximum likelihood estimation often breaks 
  down and standard procedures no longer yield correct inference. Instead, we may 
  rely on adaptive estimators of nuisance parameters to construct flexible regression estimators.
  However, use of adaptive estimators poses a challenge for performing
  statistical inference about an estimated treatment effect. While doubly-robust
  estimators facilitate inference when *all* relevant regression functions are
  consistently estimated, the same cannot be said when at least one estimator is
  inconsistent. \pkg{drtmle} implements
  doubly-robust confidence intervals and hypothesis tests about targeted minimum
  loss-based estimates of the average treatment effect. The package additionally
  implements an inverse probability of treatment weighted estimator that yields
  valid inference even when the probability of treatment is estimated via
  adaptive methods.
output: rticles::jss_article
bibliography: refs
---

>>>>

---
documentclass: jss
author:
  - name: David Benkeser
    affiliation: Emory University
    address: |
      | 1518 Clifton Road, NE
      | Mailstop: 002-3AA
      | Atlanta, Georgia, 30322, U.S.A.
    email: \email{benkeser@emory.edu}
    orcdi: 0000-0002-1019-8343
  - name: Nima S. Hejazi
    affiliation: University of California, Berkeley
    email: \email{nhejazi@berkeley.edu}
    orcdi: 0000-0002-7127-2789
title:
  formatted: "Doubly-Robust Inference in R using \\pkg{drtmle}"
  plain: "Doubly-Robust Inference in R using drtmle"
  short: "\\pkg{drtmle}: Doubly-robust Inference"
keywords:
  formatted: [causal inference, machine learning, treatment effects, targeted minimum loss estimation]
  plain: [causal inference, machine learning, treatment effects, targeted minimum loss estimation]
preamble: >
  \usepackage{amsmath}
abstract: >
  Inverse probability of treatment weighted estimators and doubly-robust
  estimators (including augmented inverse probability of treatment weight and
  targeted minimum loss-based estimators) are widely used in causal inference to
  estimate and draw inference about the average effect of a treatment. As an
  intermediate step, these estimators require estimation of key nuisance
  parameters, which are often regression functions. Typically, regressions are
  estimated using maximum likelihood and parametric models. Confidence intervals
  and p-values may be computed based on standard asymptotic results, such as the
  central limit theorem, the delta method, and the nonparametric bootstrap.
  However, in high-dimensional settings maximum likelihood estimation often
  breaks down and standard procedures no longer yield correct inference.
  Instead, we may rely on adaptive estimators of nuisance parameters to
  construct flexible regression estimators.  However, use of adaptive estimators
  poses a challenge for performing statistical inference about an estimated
  treatment effect. While doubly-robust estimators facilitate inference when
  *all* relevant regression functions are consistently estimated, the same
  cannot be said when at least one estimator is inconsistent. \pkg{drtmle}
  implements doubly-robust confidence intervals and hypothesis tests about
  targeted minimum loss-based estimates of the average treatment effect. The
  package additionally implements an inverse probability of treatment weighted
  estimator that yields valid inference even when the probability of treatment
  is estimated via adaptive methods.
output: rticles::jss_article
bibliography: refs
---
